|

### 2024-08-11 doc/paper.qmd
table formatting

print(prep_latex_table(
    em_results['final_combined_table'], 
    caption='Replicated table - Country scores for earnings management measures (Sorted by aggregate earnings management)',
    label='tab:final_combined_table'
))
```

>>>>

# Rename the 'item6026' and 'aggregate_EM_Score' columns
em_results['final_combined_table'].rename(columns={
    'item6026': 'Country',
    'Aggregate_EM_Score': 'Aggregate EM score'
}, inplace=True)

# Render the final table with the updated column names
print(prep_latex_table(
    em_results['final_combined_table'], 
    caption='Replicated table - Country scores for earnings management measures (Sorted by aggregate earnings management)',
    label='tab:final_combined_table'
))
```
